Log Journal Project Theme 9

### 2022-09-22 Resources/LogJournal.Rmd
Added a density plot but without text

---
title: "Log"
author: "J.A. Busker"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA)
library(tidyr)
library(kableExtra)
library(ggplot2)
library(gridExtra)
library(cowplot)
```

@@

1.  Sequence Name: Accession number for the SWISS-PROT database.  
2.  mcg: McGeoch's method for signal sequence recognition.  
3.  gvh: von Heijne's method for signal sequence recognition.  
4.  alm: Score of the ALOM membrane spanning region prediction program.  
5.  mit: Score of discriminant analysis of the amino acid content of the N-terminal region (20 residues long) of mitochondrial and non-mitochondrial proteins.  
6.  erl: Presence of "HDEL" substring (thought to act as a signal for retention in the endoplasmic reticulum lumen). Binary attribute.  
7.  pox: Peroxisomal targeting signal in the C-terminus.  
8.  vac: Score of discriminant analysis of the amino acid content of vacuolar and extracellular proteins.  
9.  nuc: Score of discriminant analysis of nuclear localization signals of nuclear and non-nuclear proteins.  
10. Class Distribution: The class is the localization site. Consisting of (abbreviation (full name) the amount):

        CYT (cytosolic or cytoskeletal)                    463  
        NUC (nuclear)                                      429  
        MIT (mitochondrial)                                244  
        ME3 (membrane protein, no N-terminal signal)       163  
        ME2 (membrane protein, uncleaved signal)            51  
        ME1 (membrane protein, cleaved signal)              44  
        EXC (extracellular)                                 37  
        VAC (vacuolar)                                      30  
        POX (peroxisomal)                                   20  
        ERL (endoplasmic reticulum lumen)                    5

## EDA of the yeast data

@@

```{r}
attr_names <- c("seq.name", "mcg", "gvh", "alm", "mit", "erl", "pox", "vac","nuc", "loc.site" )
data_types <- c("str", "float", "float", "float", "float", "float", "bool", "float", "float", "factor")
data_labels <- c("Accession number for the SWISS-PROT database",
                                    "McGeoch's method for signal sequence recognition", 
                                    "von Heijne's method for signal sequence recognition", 
                                    "Score of the ALOM membrane spanning region prediction program",
                                    "Score of discriminant analysis of the amino acid content of the N-terminal region",
                                    "Presence of 'HDEL' substring",
                                    "Peroxisomal targeting signal in the C-terminus",
                                    "Score of discriminant analysis of the amino acid content of vacuolar and extracellular proteins",
                                    "Score of discriminant analysis of nuclear localization signals of nuclear and non-nuclear proteins",
                                    "The class is the localization site")
codebook <- data.frame(Name=attr_names, Fullname=data_labels, Datatypes=data_types)

codebook %>%
  kbl(caption = "Codebook of the data") %>%
  kable_classic(html_font = "Cambria")
```

@@

```{r}
p1 <- ggplot(data, mapping = aes(x = "", y = gvh)) + geom_violin(alpha=0.2) + geom_jitter(width = 0.1, height = 0.1, alpha = 0.4, color = "red")

p2 <- ggplot(data, mapping = aes(x = "", y = alm)) + geom_violin(alpha=0.2) + geom_jitter(width = 0.2, height = 0.1, alpha = 0.4, color = "blue")

p3 <- ggplot(data, mapping = aes(x = "", y = mit)) + geom_violin(alpha=0.2) + geom_jitter(width = 0.2, height = 0.1, alpha = 0.4, color = "yellow")

p4 <- ggplot(data, mapping = aes(x = "", y = vac)) + geom_violin(alpha=0.2) + geom_jitter(width = 0.2, height = 0.1, alpha = 0.4, color = "green")

grid.arrange(p1, p2, nrow = 1)
grid.arrange(p3, p4, nrow = 1)
```

```{r}
p1 <- ggplot(data, (mapping = aes(x = loc.site, y = mcg))) + geom_violin(aes(color = loc.site))
p2 <- ggplot(data, (mapping = aes(x = loc.site, y = gvh))) + geom_violin(aes(color = loc.site))

grid.arrange(p1, p2, nrow = 2)
```

>>>>

---
title: 'Log Journal Project Theme 9'
author: 'J.A. Busker (352905 BFV3)'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA)
library(tidyr)
library(kableExtra)
library(ggplot2)
library(gridExtra)
library(cowplot)
library(ggpubr)
library(pander)
library(ggbiplot)
```

@@

* **Sequence Name**: Accession number for the SWISS-PROT database.  
* **mcg**: McGeoch's method for signal sequence recognition.  
* **gvh**: von Heijne's method for signal sequence recognition.  
* **alm**: Score of the ALOM membrane spanning region prediction program.  
* **mit**: Score of discriminant analysis of the amino acid content of the N-terminal region (20 residues long) of mitochondrial and non-mitochondrial proteins.  
* **erl**: Presence of "HDEL" substring (thought to act as a signal for retention in the endoplasmic reticulum lumen). Binary attribute.  
* **pox**: Peroxisomal targeting signal in the C-terminus.  
* **vac**: Score of discriminant analysis of the amino acid content of vacuolar and extracellular proteins.  
* **nuc**: Score of discriminant analysis of nuclear localization signals of nuclear and non-nuclear proteins.  
* **Class Distribution**: The class is the localization site. Consisting of (abbreviation (full name) the amount):

--- ---------------------------------------------- ---
CYT (cytosolic or cytoskeletal)                    463  
NUC (nuclear)                                      429  
MIT (mitochondrial)                                244  
ME3 (membrane protein, no N-terminal signal)       163  
ME2 (membrane protein, uncleaved signal)            51  
ME1 (membrane protein, cleaved signal)              44  
EXC (extracellular)                                 37  
VAC (vacuolar)                                      30  
POX (peroxisomal)                                   20  
ERL (endoplasmic reticulum lumen)                    5  
--- ---------------------------------------------- --

@@

```{r}
attr_names <- c("seq.name", "mcg", "gvh", "alm", "mit", "erl",
                "pox", "vac","nuc", "loc.site" )

data_types <- c("str", "float", "float", "float", "float", "float",
                "bool", "float", "float", "factor")

data_labels <- c("Accession number for the SWISS-PROT database",
                 "McGeoch's method for signal sequence recognition",
                 "von Heijne's method for signal sequence recognition",
                 "Score of the ALOM membrane spanning region prediction program",
                 "Score of discriminant analysis of the amino 
                 acid content of the N-terminal region",
                 "Presence of 'HDEL' substring",
                 "Peroxisomal targeting signal in the C-terminus",
                 "Score of discriminant analysis of the amino acid content 
                 of vacuolar and extracellular proteins",
                 "Score of discriminant analysis of nuclear 
                 localization signals of nuclear and non-nuclear proteins",
                 "The class is the localization site")

codebook <- data.frame(Name=attr_names, 
                       Fullname=data_labels, 
                       Datatypes=data_types)

pander(codebook)
```

@@

```{r}
p1 <- ggplot(data, mapping = aes(x = "", y = mcg)) + geom_violin(alpha=0.2) + 
  geom_jitter(width = 0.1, height = 0.1, alpha = 0.4, color = "red")

p2 <- ggplot(data, mapping = aes(x = "", y = gvh)) + geom_violin(alpha=0.2) + 
  geom_jitter(width = 0.2, height = 0.1, alpha = 0.4, color = "blue")

ggarrange(p1, p2, nrow = 1)
```

```{r}
p3 <- ggplot(data, mapping = aes(x = "", y = alm)) + geom_violin(alpha=0.2) + 
  geom_jitter(width = 0.1, height = 0.1, alpha = 0.4, color = "red")

p4 <- ggplot(data, mapping = aes(x = "", y = mit)) + geom_violin(alpha=0.2) + 
  geom_jitter(width = 0.2, height = 0.1, alpha = 0.4, color = "blue")

ggarrange(p3, p4, nrow = 1)
```

```{r}
p5 <- ggplot(data, mapping = aes(x = "", y = pox)) + geom_violin(alpha=0.2) + 
  geom_jitter(width = 0.2, height = 0.1, alpha = 0.4, color = "yellow")

p6 <- ggplot(data, mapping = aes(x = "", y = vac)) + geom_violin(alpha=0.2) + 
  geom_jitter(width = 0.2, height = 0.1, alpha = 0.4, color = "green")

ggarrange(p5, p6, nrow = 1)
```

```{r}
p1 <- ggplot(data, aes(x=mcg)) + geom_density(aes(color=loc.site)) + theme(legend.position = "none")
p2 <- ggplot(data, aes(x=gvh)) + geom_density(aes(color=loc.site)) + theme(legend.position = "none")
p3 <- ggplot(data, aes(x=alm)) + geom_density(aes(color=loc.site)) + theme(legend.position = "none")
p4 <- ggplot(data, aes(x=mit)) + geom_density(aes(color=loc.site)) + theme(legend.position = "none")
p5 <- ggplot(data, aes(x=pox)) + geom_density(aes(color=loc.site)) + theme(legend.position = "none")
p6 <- ggplot(data, aes(x=vac)) + geom_density(aes(color=loc.site)) + theme(legend.position = "none")
ggarrange(p1, p2, p3, p4, p5, p6, ncol=3, nrow=2, common.legend=TRUE, legend="right")
```
